The \project{unRAVE} catalog

### 2016-08-15 article/unrave.tex
Minor things

\title{The \project{UNRAVE} catalog}

@@

\begin{abstract}
On 14 September 2016 the \project{Gaia} mission will release positions, proper 
motions, and parallaxes for about two million stars.  Most studies intending to
make use of those data would benefit enormously by coupling that astrometry with
stellar chemical abundances.  The RAdial Velocity Experiment (\project{RAVE}) 
survey has acquired spectra for approximately 290,000 stars in common with the 
first \project{Gaia} data release, constituting the largest overlap of any 
stellar spectroscopic sample.  Here we perform an independent analysis of the 
\project{RAVE} spectra using a new non-parametric implementation of \thecannon\ 
that employs prior probabilities on atomic line formation and stellar 
astrophysical parameters.  We deliver effective temperature $\teff$, surface 
gravity $\logg$, and chemical abundances of up to seven elements (Mg, Al, Si, 
Ca, Ti, Fe, Ni) for \Nstars\ stars.  We validate our results internally from 
repeat visits, and externally against existing high-resolution spectroscopic 
surveys.  The typical precision in chemical abundances is $X.XX$~dex.  
\end{abstract}

@@

As the name implies, the \rave\ survey was principally designed to obtain radial
velocity measurements for up to $10^6$ stars.  Detailed chemical abundances were
a secondary science goal of the survey.  For this reason the distribution
of S/N ratios for \rave\ spectra is considerably lower than stellar 
spectroscopic surveys where chemical abundances are the defining objective.  The 
\rave\ spectra cover $\approx38$~nm in the infrared with an effective resolution
$\mathcal{R} \approx 7500$, and the S/N peaks at $\approx$50~per~pixel$^{-1}$.
For comparison, the \project{GALAH} survey \citep{DeSilva_2015} --- which was 
specifically constructed for detailed chemical abundance analyses --- includes a
wavelength range about 2.5 times larger at resolution $\mathcal{R} \approx 28,000$,
and target for S/N $\gtrsim100$.

@@

@@

% Chi-sq of the sample.
% Identify outliers.
% Convex hull?

@@

\acknowledgements
We thank Sven Buder (MPIA), others??.
This research made use of: Astropy, a community-developed core Python package for
Astronomy \citep{astropy}, NASA's Astrophysics Data System Bibliographic Services;
 and \project{TOPCAT} \citep{Taylor2005}.
This work was partly supported by the European Union FP7 programme through ERC 
grant number 320360.
Funding for RAVE has been provided by: the Australian Astronomical Observatory; the Leibniz-Institut fuer Astrophysik Potsdam (AIP); the Australian National University; the Australian Research Council; the French National Research Agency; the German Research Foundation (SPP 1177 and SFB 881); the European Research Council (ERC-StG 240271 Galactica); the Istituto Nazionale di Astrofisica at Padova; The Johns Hopkins University; the National Science Foundation of the USA (AST-0908326); the W. M. Keck foundation; the Macquarie University; the Netherlands Research School for Astronomy; the Natural Sciences and Engineering Research Council of Canada; the Slovenian Research Agency; the Swiss National Science Foundation; the Science \& Technology Facilities Council of the UK; Opticon; Strasbourg Observatory; and the Universities of Groningen, Heidelberg and Sydney. The RAVE web site is https://www.rave-survey.org.

@@

\bibitem[Taylor(2005)]{Taylor2005} Taylor, M.~B.\ 2005, Astronomical Data Analysis Software and Systems XIV, 347, 29

@@

\begin{figure}[p]
\caption{The RMS of the test set labels as a function of S/N ratio for repeated stars in the test set.\label{fig:test-set-repeats}}
\end{figure}

\begin{figure}[p]
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{RAVE} fourth data release.\label{fig:dr4-comparison}}
\end{figure}

\begin{figure}[p]
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{Gaia-ESO Survey} fourth internal data release.\label{fig:dr4-comparison}}
\end{figure}

\begin{figure}[p]
\caption{Stellar label comparisons between the \project{UNRAVE} catalog and the samples discussed in \citep{Kordopatis_2013}}
\end{figure}

>>>>

\title{The \project{unRAVE} catalog}

@@

\begin{abstract}
On 14 September 2016 the \project{Gaia} mission will release positions, proper 
motions, and parallaxes for about two million stars.  Most studies intending to
make use of those data would benefit enormously by coupling that astrometry with
stellar chemical abundances.  The RAdial Velocity Experiment (\project{RAVE}) 
survey has acquired spectra for approximately 290,000 stars in common with the 
first \project{Gaia} data release, constituting the largest overlap of any 
stellar spectroscopic sample.  Here we perform an independent analysis of the 
\project{RAVE} spectra using a new non-parametric implementation of \thecannon\ 
that employs prior probabilities on atomic line formation and stellar 
astrophysical parameters.  We deliver effective temperature $\teff$, surface 
gravity $\logg$, and chemical abundances of up to seven elements (Mg, Al, Si, 
Ca, Ti, Fe, Ni) for \Nstars\ stars.  We validate our results internally from 
repeat visits, and externally against existing high-resolution spectroscopic 
surveys.  The typical precision in chemical abundances is X.XX~dex.  
\end{abstract}

@@

As the name implies, the \rave\ survey was principally designed to obtain radial
velocity measurements.  Detailed chemical abundances were a secondary science 
goal of the survey.  For this reason the distribution of S/N ratios for \rave\ 
spectra is considerably lower than stellar spectroscopic surveys where chemical
abundances are the defining objective.  The 
\rave\ spectra cover $\approx38$~nm in the infrared with an effective resolution
$\mathcal{R} \approx 7500$, and the S/N peaks at $\approx$50~per~pixel$^{-1}$.
For comparison, the \project{GALAH} survey \citep{DeSilva_2015} --- which was 
specifically constructed for detailed chemical abundance analyses --- includes a
wavelength range about 2.5 times larger at resolution $\mathcal{R} \approx 28,000$,
and target for S/N $\gtrsim100$.

@@

% Inserting 2MASS photometry as fake pixels

@@

% Chi-sq of the sample.
% Identify outliers.
% Convex hull? Distance to plane?

@@

\acknowledgements
We thank Sven Buder (MPIA), others??.
This research made use of: Astropy, a community-developed core Python package for
Astronomy \citep{astropy}, NASA's Astrophysics Data System Bibliographic Services;
and \project{TOPCAT} \citep{Taylor_2005}.
This work was partly supported by the European Union FP7 programme through ERC 
grant number 320360.
Funding for RAVE has been provided by: the Australian Astronomical Observatory; 
the Leibniz-Institut fuer Astrophysik Potsdam (AIP); the Australian National 
University; the Australian Research Council; the French National Research Agency;
the German Research Foundation (SPP 1177 and SFB 881); the European Research 
Council (ERC-StG 240271 Galactica); the Istituto Nazionale di Astrofisica at 
Padova; The Johns Hopkins University; the National Science Foundation of the USA
(AST-0908326); the W. M. Keck foundation; the Macquarie University; the 
Netherlands Research School for Astronomy; the Natural Sciences and Engineering 
Research Council of Canada; the Slovenian Research Agency; the Swiss National 
Science Foundation; the Science \& Technology Facilities Council of the UK; 
Opticon; Strasbourg Observatory; and the Universities of Groningen, Heidelberg 
and Sydney. The RAVE web site is https://www.rave-survey.org.

@@

\bibitem[Taylor(2005)]{Taylor_2005} Taylor, M.~B.\ 2005, Astronomical Data Analysis Software and Systems XIV, 347, 29

@@

\begin{figure*}[p]
\caption{The RMS of the test set labels as a function of S/N ratio for repeated stars in the test set.\label{fig:test-set-repeats}}
\end{figure*}

\begin{figure*}[p]
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{RAVE} fourth data release.\label{fig:rave-dr4-comparison}}
\end{figure*}

\begin{figure*}[p]
\caption{Stellar label comparison between the \project{UNRAVE} catalog and the \project{Gaia-ESO Survey} fourth internal data release.\label{fig:ges-dr4-comparison}}
\end{figure*}

\begin{figure*}[p]
\caption{Stellar label comparisons between the \project{UNRAVE} catalog and the samples discussed in \citep{Kordopatis_2013}}
\end{figure*}
